Choose a License

### 2025-01-25 about.qmd
Only license code as CC0
This makes it less complicated to describe,
although we deviate now from our
recommendations (regarding CC0's lack of patent
grant).

Except where noted otherwise, the material in this tutorial is licensed under [CC\ BY-SA\ 4.0](https://creativecommons.org/licenses/by-sa/4.0/); the code chunks are also (at your option) available under [CC0\ 1.0](https://creativecommons.org/publicdomain/zero/1.0/) or the [Apache License\ 2.0](https://www.apache.org/licenses/LICENSE-2.0).

>>>>

Except where noted otherwise, the material in this tutorial is licensed under [CC\ BY-SA\ 4.0](https://creativecommons.org/licenses/by-sa/4.0/); the code chunks are also (at your option) available under [CC0\ 1.0](https://creativecommons.org/publicdomain/zero/1.0/).

### 2025-01-25 choose_license.qmd
Only license code as CC0
This makes it less complicated to describe,
although we deviate now from our
recommendations (regarding CC0's lack of patent
grant).

The manuscript you downloaded for this tutorial is made available to you under [CC0\ 1.0](https://creativecommons.org/publicdomain/zero/1.0/) or (at your option) under the [Apache License\ 2.0](https://www.apache.org/licenses/LICENSE-2.0), as is all code in this tutorial (e.g., for creating the data dictionary). Therefore, you can apply any license to your modified version (as long as you follow the terms of the existing license). Please apply the license of your choice now, using any of the methods mentioned above (except the `README`, which we will cover later).

@@

In the following example, the files from this tutorial are used under the terms of CC0\ 1.0 and therefore, the requirements of the Apache license\ 2.0 need not be followed.

The edited manuscript files have been multi-licensed under [AGPLv3](https://www.gnu.org/licenses/agpl-3.0.html) (or later) or (at option of the reuser) under [CC\ BY-SA\ 4.0](https://creativecommons.org/licenses/by-sa/4.0/), while the data dictionary and its code are made available under CC0\ 1.0.

>>>>

The manuscript you downloaded for this tutorial is made available to you under [CC0\ 1.0](https://creativecommons.org/publicdomain/zero/1.0/) as is all code in this tutorial (e.g., for creating the data dictionary). Therefore, you can apply any license to your modified version. Please apply the license of your choice now, using any of the methods mentioned above (except the `README`, which we will cover later).

@@

In the following example, the edited manuscript files have been multi-licensed under [AGPLv3](https://www.gnu.org/licenses/agpl-3.0.html) (or later) or (at option of the reuser) under [CC\ BY-SA\ 4.0](https://creativecommons.org/licenses/by-sa/4.0/), while the data dictionary and its code are made available under CC0\ 1.0.
